Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-02-15 ms.tex
working on the intro

@@

\marginpar{Talk here about likelihood structure---the `gaussian on a cylinder' concept, why we would want to project out the phase error.}%
%
A wrinkle is that $\mathcal{I}_{\tau\tau}$ depends on the true value of $\rho$. If we make the further leap of evaluating the \ac{CRLB} \emph{at the value of the estimators}, we can write
%
\begin{eqnarray}
    \hat{\rho} - \rho \sim \mathcal{N}\, [0, 1] \\
    \hat{\gamma} - \gamma \sim \mathcal{N}\, \left[0, \overline{\omega^2} / {\omega_\mathrm{rms}}^2\right] \\
    \hat{\tau} - \tau \sim \mathcal{N} \left[0, 1 / {\omega_\mathrm{rms}}^2\right].
\end{eqnarray}

@@

The marginalization over $D_\mathrm{L}$, $x$, and $\psi$ must be done numerically. The outermost integration is over x and $\psi$, and is done with Newton-Cotes by evaluating $\mathcal{L}_\mathrm{SNR}$ on a regular lattice in $x$ and $\psi$. This integration scheme is first order in $x$ and second order in $\psi$.

>>>>

\section{Introduction}

Ground-based gravitational-wave interferometers are entering the advanced detector era, positioning themselves to make profound discoveries about the universe.  The advanced LIGO and Vigo detectors will be part of a worldwide network that also includes KAGRA and hopefully LIGO-India.  Coalescing neutron star binaries are among the most likely sources, with event rates of $~ 50/\mathrm{yr}$ (check that number!).  In addition to the ....(do we want to review emission mechanisms?)

In this paper we present a method of rapid sky localization that makes use of Bayesian methods.  It differs from

@@

\marginpar{Talk here about likelihood structure---the `gaussian on a cylinder' concept, why we would want to project out the phase error.}%
%
A wrinkle is that $\mathcal{I}_{\tau\tau}$ depends on the true values of $\rho_A$ and $\rho_B$. If we make the further leap of evaluating the \ac{CRLB} \emph{at the value of the estimators}, we can write
%
\begin{eqnarray}
    \hat{\rho} - \rho \sim \mathcal{N}\, [0, 1] \\
    \hat{\gamma} - \gamma \sim \mathcal{N}\, \left[0, \overline{\omega^2} / {\omega_\mathrm{rms}}^2\right] \\
    \hat{\tau} - \tau \sim \mathcal{N} \left[0, 1 / {\omega_\mathrm{rms}}^2\right].
\end{eqnarray}

@@

The marginalization over $D_\mathrm{L}$, $x$, and $psi$ must be done numerically. The outermost integration is over x and $\psi$, and is done with Newton-Cotes by evaluating $\mathcal{L}_\mathrm{SNR}$ on a regular lattice in $x$ and $\psi$. This integration scheme is first order in $x$ and second order in $\psi$.
